A Study on Penguins: A Minimal Reproducible Example

### 2024-08-23 01_Example/Manuscript.qmd
Show summary statistics by sex rather than species
Fix missing decimal point
See https://github.com/quarto-dev/quarto-cli/issues/10595

modelsummary::datasummary_balance(formula = ~ species, data = data_clean, dinm = FALSE)

@@

The t-test revealed a significant difference in bill lengths between male and female penguins ($t(`{r} round(t_test_result$parameter, digits = 2)`) = `{r} round(t_test_result$statistic, digits = 2)`, p `{r} format.pval(t_test_result$p.value, eps = 0.001, scientific = FALSE)`$).
Female penguins ($M = `{r} round(mean(blm_female), digits = 2)`\,\mathrm{mm}, SD = `{r} round(sd(blm_female), digits = 2)`\,\mathrm{mm}$) exhibited shorter bill lengths compared to male penguins ($M = `{r} round(mean(blm_male), digits = 2)`\,\mathrm{mm}, SD = `{r} round(sd(blm_male), digits = 2)`\,\mathrm{mm}$).

>>>>

modelsummary::datasummary_balance(formula = ~ sex, data = data_clean, dinm = FALSE)

@@

The t-test revealed a significant difference in bill lengths between male and female penguins ($t(`r round(t_test_result$parameter, digits = 2)`) = `r round(t_test_result$statistic, digits = 2)`, p `r format.pval(t_test_result$p.value, eps = 0.001, scientific = FALSE)`$).
Female penguins ($M = `r round(mean(blm_female), digits = 2)`\,\mathrm{mm}, SD = `r round(sd(blm_female), digits = 2)`\,\mathrm{mm}$) exhibited shorter bill lengths compared to male penguins ($M = `r round(mean(blm_male), digits = 2)`\,\mathrm{mm}, SD = `r round(sd(blm_male), digits = 2)`\,\mathrm{mm}$).
